Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-14 paper/ms.tex
minor changes in the paper and referee report

>>>>

 To keep the validity of Eq. (\ref{eq:width}) there should be of the order of
 $27$ field or even a larger number. Each of these fields should have  $\sim1{\rm
  deg^2}$ in size and reproduce the same observational conditions of 
  \citet{Bielby16} in terms of filters, equivalent
width cuts .  However, repeating the same kind of cosmic variance 
study for different survey strategies should help to provide a equivalent
constraint.
